Analysis of Fraxinus Player stats
========================================================

Background
--------------------------------------------------------
Each Fraxinus player user access stats are printed such as number of days they are active and number pattern alignments they have attempted during the period

Resulting file has following header  
* `"UserId"   "NoofDays"  "TotalTasks"  "MeanTaskperDay"    "FBScore"   "FBBonus"   "FBID"`  

Meaning of the terms used in the headers mentioned above:

| Term              | Definition                                                                                                                            |
|:----------------- |:------------------------------------------------------------------------------------------------------------------------------------  |
| UserId            | User Id number                                                                                                                            |
| NoofDays	        |	Number of days user has actively visited Fraxinus                                                                                          |
| TotalTasks        |	Total number of pattern alignmnets perfomred by the User                                                  |
| MeanTaskperDay	  |	Mean tasks per day                                                                                                     |
| FBScore           |	Points scored in Facebook  | 
| FBBonus           | Total number of bonus points achieved  | 
| FBID              | Facebook User Id  | 

Analysis
--------------------------------------------------------
Resulting table was loaded in to R and the plots are generated to observe the trends in user alignments

Load libraries and the datage
```{r setup, include=FALSE}
opts_chunk$set(dev = 'pdf')
library(ggplot2)
library(gridExtra)
user_data <- read.delim("users_progress_report.txt", header=T)

```

There are 
## `r length(user_data$UserId)` 
players have accesssed Fraxinus


### Distribution of number of active days from all players:

```{r fig.width=7, fig.height=6}
ggplot(data=user_data, aes(NoofDays)) + geom_histogram(binwidth=1) + scale_y_sqrt() + ggtitle("Distribution of no. of active days from all players")

```


### Distribution of number of alignment task from all palyers:

```{r fig.width=7, fig.height=6}
ggplot(data=user_data, aes(TotalTasks)) + geom_histogram(binwidth=10) + scale_y_sqrt() + ggtitle("Distribution of no. of alignment tasks from all players")

```


### Distribution of mean number of alignment task per day from all palyers:

```{r fig.width=7, fig.height=6}
ggplot(data=user_data, aes(TotalTasks/NoofDays)) + geom_histogram(binwidth=10) + scale_y_sqrt() + ggtitle("Distribution of mean no. of alignment tasks per day from all players")

```


### Distribution of facebook scores from all players:

```{r fig.width=7, fig.height=6}
ggplot(data=user_data, aes(FBScore)) + geom_histogram(binwidth=10) + scale_y_sqrt() + ggtitle("Facebook scores from all players")

```


### Distribution of frequency days:

```{r fig.width=14, fig.height=6}
user_data <- user_data[order(user_data$NoofDays, decreasing = TRUE),]
user_data$Rank <- c(1:length(user_data$UserId))
ggplot(data=user_data, aes(Rank, NoofDays)) + geom_point() + scale_x_log10() + scale_y_log10() + ggtitle("Log-log distribution")

```


### Distribution of frequency tasks:

```{r fig.width=14, fig.height=6}
user_data <- user_data[order(user_data$TotalTasks, decreasing = TRUE),]
user_data$Rank <- c(1:length(user_data$UserId))
ggplot(data=user_data, aes(Rank, TotalTasks)) + geom_point() + scale_x_log10() + scale_y_log10() + ggtitle("Log-log distribution")

```

### Distribution of frequency FBScore:

```{r fig.width=14, fig.height=6}
user_data <- user_data[order(user_data$FBScore, decreasing = TRUE),]
user_data$Rank <- c(1:length(user_data$UserId))
ggplot(data=user_data, aes(Rank, FBScore)) + geom_point() + scale_x_log10() + scale_y_log10() + ggtitle("Log-log distribution")

```



